Component-based Software Development Framework \\for Embedded IoT Devices（仮）

### 2017-11-14 ipsj/paper.tex
Add TLSF+TECS's use cases
Add mruby's use case

\subsection{Extended mruby on TECS (仮)}

\textcolor{red}{TODO: mrubyからTINETを利用する説明とかmrubyでエコーサーバのコード例とか}

@@

%4
\section{Evaluation}
\label{sec:Evaluation}

>>>>

@@

%4
\subsection{Use case}
\label{sec:UseCase}

In the proposed framework, applications can call TINET functions such as TCP and UDP from mruby programs because mruby-TECS bridge automatically generates the code linking mruby and C.
Fig.\ref{src:mruby} shows an mruby program to transmit the value acquired from a sensor.
mruby makes it easier to develop applications than existing TINET, i.e., C language.

In the case of a simple application, a few functions are only used and there are some unused functions.
For example, the application only uses a function to send by TCP protocol as shown in Fig.\ref{src:mruby}.
The proposed framework incorporates TINET+TECS, and can easily custimize such as removing UDP functions, supporting only IPv4, or removing TCP receiving function.
It can be applied to embedded systems with strict memory constraints by removing unused functions.

\begin{figure}[t]
\centering
\begin{lstlisting}
begin
    io = AnalogIO.new(A0, INPUT)
    cep = TCP.new()	
    cep.accept
    loop do		
        val = io.read  
        cep.snd val.to_s + "\n"		
        RTOS.delay(1000)			
    end
rescue => e	
    puts "[ERROR]" + e
end
\end{lstlisting}
\caption{Example of mruby application}
\label{src:mruby}
\end{figure}

\section{Evaluation}
\label{sec:Evaluation}
